---
title: "p8105_hw1_bf2506"
output: html_document
date: "2022-09-17"
---

```{r tidy, include=FALSE}
library(tidyverse) #Load tidyverse
```


### Prolem 1

#### Download the package containing penguins dataset in console and load this dataset
```{r load_data, include=FALSE}
data("penguins", package = "palmerpenguins")
```

```{r show_data}
penguins
```

**·** Penguins dataset cotains **8** varaibles, which is *"species"*, *"island"*, *"bill_length_mm"*, *"bill_depth_mm"*, *"flipper_length_mm"*, *"body_mass_g"*, *"sex"*, *"year"*.

**·** The size of the dataset is **`r nrow(penguins)` rows** and **`r ncol(penguins)` columns**.


```{r drop_missing_values, include=FALSE}
nonna_flipper=drop_na(penguins,flipper_length_mm)
```

**·** And we calculate the **mean flipper length** is `r  mean(nonna_flipper$flipper_length_mm)`(*missing values are removed*)

#### Here is a **scatter plot of flipper_length_mm (y) vs bill_length_mm (x)**

```{r scatterplot_fli/bill, echo=FALSE, message=FALSE, warning=FALSE}

ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()

ggsave("scatter_plot.pdf", height = 4, width = 6)
```

### Problem 2

#### Create a data frame

```{r problem2_df, echo=FALSE, message=FALSE, warning=FALSE}
set.seed(1)

problem2_df = tibble(
  vec_numeric = rnorm(10),
  
  vec_logical = vec_numeric > 0,
  
  vec_char = c("I", "like", "R", "studio", "very", "much", "D", "O", "G", "E"),
  
  vec_factor = factor(c("fail", "pass", "good", "good", "pass", "pass", "fail", "good", "good", "good"))
)

problem2_df
```
 
#### Take the mean of a variable in problem2_df
```{r mean, message=FALSE, warning=FALSE, include=FALSE}
trial_num = mean(problem2_df$vec_numeric)
trial_log = mean(problem2_df$vec_logical)
trial_char = mean(problem2_df$vec_char)
trial_fac = mean(problem2_df$vec_factor)
```

**·**The mean of vec_numeric is `r trial_num`,  
**·**The mean of vec_logical is `r trial_log`,  
**·**The mean of vec_char is `r trial_char`,  
**·**The mean of vec_factor is `r trial_fac`.

**numeric and logical** vector works and **character and factor** vectors doesn’t work.

#### Convert variables
```{r transfer_to_num, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}
vec_logical = as.numeric(problem2_df$vec_logical)
vec_char = as.numeric(problem2_df$vec_char)
vec_factor = as.numeric(problem2_df$vec_factor)
vec_logical
vec_char
vec_factor
```
**logical and factor** vector can be convert to a numeric type but **character** vectors can not.  

**·**I think logical variables and factor variables can be converted to numeric type is because we can use numbers to present their meanings, but there is no rule for character variables

**·**When we calculate the mean, numeric variables and logical variables have corresponding numeric meanings to be calculated, but factor variables and character variables do not.
