---
title: "p8105_hw1_bf2506"
output: html_document
date: "2022-09-17"
---
#Prolem 1


Download the a package containing the penguins dataset in console and  load the penguins dataset
```{r load_data, include=FALSE}
data("penguins", package = "palmerpenguins")
```

```{r show_data}
penguins
```

**路** Penguins dataset cotains **8** varaibles, which is *"species"*, *"island"*, *"bill_length_mm"*, *"bill_depth_mm"*, *"flipper_length_mm"*, *"body_mass_g"*, *"sex"*, *"year"*.

**路** The size of the dataset is **`r nrow(penguins)` rows** and **`r ncol(penguins)` columns**.


```{r drop_missing_values, include=FALSE}
library(tidyverse)
nonna_flipper=drop_na(penguins,flipper_length_mm)
```

**路** And we calculate the **mean flipper length** is `r  mean(nonna_flipper$flipper_length_mm)`(*missing values are removed*)

**路**Here is a scatter plot of flipper_length_mm (y) vs bill_length_mm (x)

```{r scatterplot_fli/bill, echo=FALSE, message=FALSE, warning=FALSE}

ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()
```

